---
title: "Who does more pushups"
author: "Freida Nockideneh"
date: "October 7, 2017"
output: html_document
---

```{r include=FALSE}
require(knitr)
require(mosaic)
require(tigerstats)
```
<!-- We recommend you use git branches -- create a separate branch for each major section i.e. Introduction, Methods, Results, Inferential Results, and Discussion and Conclusions - leave the YAML block untouched until the final merge where you put in your own name !-->

# Introduction

Several years ago some MAT 111 students who were on the footbal team conducted a study of their team-mates.  The results are contained in the data frame `pushups` in the `tigerstats` package.

```{r eval=FALSE}
data(pushups)
View(pushups)
help(pushups)
```

Among other things, the students recorded the type of position a player had on the team (either line or skill), and also the number of push-ups each player could perform in a two-minute period.

Line players are on the offensive or defensive line.  They need to be a certain kind of speed, but they must also be quite big and strong.  Skill players do a lot of runninga and catching:  they are the quarterback, running backs, receivers, etc.

Our Research Question is:

  >Who does more pushups, on average: a line player or a skill player?


# Methods
<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

I used view pushups for my method. Linemen (skill) do more pushups than linebacks (line) because they run around more and they weight lighter than linebacks. 

# Results
<!--You have both graphical and numerical methods, so you will have both graphical and numerical results to consider.!-->
From my box plot and numerical results, Skill positions do more pushups. 

## Graphical Results
<!--Your graph should have a good title, and axes should be labled as needed.  Discuss your graphical results, showing how they answer the research question.  Use specific features of the graph in your discussion.!-->
```{r}

counts <- table(pushups$weight)
boxplot(pushups~position,data = pushups, main="Freida's Box Graph #1", 
  	xlab="Number of Pushups")
```


## Numerical Results
<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
favstats(pushups~position,data=pushups)
```


# Inferential Results
<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

```{r}
t.test(pushups~position, data = pushups)
```

-Not true, because it's not 1 in million chance to use our data for true results. P-value is not true. 
From all my graphs and charts, SKILL players do more pushups maybe due their weight(main factor) and their position they are put into due to their weight. LINE players weight more and do less pushups, all there numbers from my results show they do less as factor to their weight too. 


# Discussion and Conclusion
<!--State your overall conclusion.  This is also a good place to mention other Research Questions that came to mind as you were carrying out this study.!-->

I really hope I did think in some of right direction. I like making the box plots and other graphs, some of them are complicating but I like figuring the simplies form and building them. I do clearly see that Skill players do more pushups than Line players. / Thank you for helping with this assignment, I hope this helps me. (I do see that Skill players from the results I got today still do more pushups and p-value.)